\vfill World of Warcraft's New Way to Get You Hooked

### 2013-04-04 paper.tex
13. Subheadings for Public Good Improvement

@@

In a case study of five ``problematic'' internet and game users, users who are seen by family and friends as having extreme computer addiction issues, only two showed signs of true addiction while the remaining three seemed to be using the internet to counter-act other deficiencies. \cite{IsThereEvidenceOfInternetAddiction} These three users who were not psychologically addicted used the internet and games to connect with others in ways they couldn't previously. Factors keeping them from doing so prior were due to physical appearance, social anxiety, and mental disability. One European man found a wife in the United States and moved to be with her, improving both their lives, thanks to his extended internet use. \cite{IsThereEvidenceOfInternetAddiction} These people use the internet and games as a way to enrich their lives, not detract from them.

During a panel at D.I.C.E. 2012 \cite{DICEInterview} that included Mike Epps, President of Epic Games, Ted Price, CEO and Founder of Insomniac Games, and Frank Pearce, current VP of product development and one of the three founders of Blizzard, Frank Pearce discussed a letter he received from a fan who had a disability and found comfort in World of Warcraft. He went on to say that Blizzard Entertainment is doing so many people a service that they actually receive letters thanking them for making such an immersive experience. \cite{DICEInterview}

In a three year study of over 30,000 MMORPG users, over 50\% of users said that they learned valuable leadership skills that have helped them outside of the game. \cite{MotivationsAndDerviedExperiences}
Many features in World of Warcraft drive the players to socialize. \footnote{Having over two months of play time in-game with the last play session less than a week ago, I consider myself qualified to discuss the mechanics of World of Warcraft without citation.} The best gear and most prestigious titles are only available to users who group together to take on challenges that cannot be conquered by oneself. These challenges require intense coordination and communication as well as skilled players. Without grouping together, players have no chance of getting these items or attaining these statuses.
Guilds offer perks to their members through mechanics built into the game. As guilds grow in size and their members complete quests and dungeons, these guilds level up and offer a variety of rewards. Becoming part of a community of people is rewarded in-game.

>>>>

\setcounter{secnumdepth}{5}

@@

\paragraph{Users Counteract Disabilities and Deficiencies\\}
In a case study of five ``problematic'' internet and game users, users who are seen by family and friends as having extreme computer addiction issues, only two showed signs of true addiction while the remaining three seemed to be using the internet to counter-act other deficiencies. \cite{IsThereEvidenceOfInternetAddiction} These three users who were not psychologically addicted used the internet and games to connect with others in ways they couldn't previously. Factors keeping them from doing so prior were due to physical appearance, social anxiety, and mental disability. One European man found a wife in the United States and moved to be with her, improving both their lives, thanks to his extended internet use. \cite{IsThereEvidenceOfInternetAddiction} These people use the internet and games as a way to enrich their lives, not detract from them.

\paragraph{Blizzard Gets Thank-You Letters\\}
During a panel at D.I.C.E. 2012 \cite{DICEInterview} that included Mike Epps, President of Epic Games, Ted Price, CEO and Founder of Insomniac Games, and Frank Pearce, current VP of product development and one of the three founders of Blizzard, Frank Pearce discussed a letter he received from a fan who had a disability and found comfort in World of Warcraft. He went on to say that Blizzard Entertainment is doing so many people a service that they actually receive letters thanking them for making such an immersive experience. \cite{DICEInterview}

\paragraph{World Of Warcraft Teaches Players Life Skills\\}
In a three year study of over 30,000 MMORPG users, over 50\% of users said that they learned valuable leadership skills that have helped them outside of the game. \cite{MotivationsAndDerviedExperiences}
Many features in World of Warcraft drive the players to socialize. \footnote{Having over two months of play time in-game with the last play session less than a week ago, I consider myself qualified to discuss the mechanics of World of Warcraft without citation.} The best gear and most prestigious titles are only available to users who group together to take on challenges that cannot be conquered by oneself. These challenges require intense coordination and communication as well as skilled players. Without grouping together, players have no chance of getting these items or attaining these statuses.
Guilds offer perks to their members through mechanics built into the game. As guilds grow in size and their members complete quests and dungeons, these guilds level up and offer a variety of rewards. Becoming part of a community of people is rewarded in-game.
